\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-03-16 write_up/mixfishsim_ecolmod.tex
Update abstract wordcount
Small textual changes

[233 words]

@@

We parameterised the simulation model for four populations with differing
habitat preference and temperature tolerances (Figures \ref{S-fig:1},
\ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
population demographic and recruitment functions; each of the populations also
has two defined spawning areas (Figure \ref{S-fig:2}) and movement rates (Table
\ref{tab:1}). The actual movement of the populations for a number of weeks is
shown in Figure \ref{S-fig:9} while the realised daily fishing mortality are
shown in Figure \ref{S-fig:10}. \\

>>>>

[333 words]

@@

We parameterised the simulation model for four populations with differing
habitat preference and temperature tolerances (Figures \ref{S-fig:1},
\ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
population demographic and recruitment functions. In addition, each of the
populations has two defined spawning areas which result in the populations
moving towards these areas in given weeks (Figure \ref{S-fig:2}) and
population-specific movement rates (Table \ref{tab:1}). The realised movement
of the populations for a number of weeks is shown in Figure \ref{S-fig:9} while
the realised daily fishing mortality are shown in Figure \ref{S-fig:10}. \\
